Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-04 article/article-draft.tex
Added back in code to filter identical clusters

\begin{table}
\centering
\caption{Top 10 Article Pair Titles}
\begin{tabular}{| l | c |}
    \hline
    \textbf{Article ID} & \textbf{Title} \\ \hline
    21986867 & 2000 New Year Honours \\ \hline
    21986897 & 1999 New Year Honours \\ \hline
    3951586 & Instruments of the United Kingdom, 1994 \\ \hline
    3951664 & Instruments of the United Kingdom, 1995 \\ \hline
    1903966 & Management of baldness \\ \hline
    38088660 & Management of androgenic alopecia \\ \hline
    1503105 & Jayne Torvill \\ \hline
    1503115 & Christopher Dean \\ \hline
    184843 & Henry VI, Part 1 \\ \hline
    184846 & Henry VI, Part 2 \\ \hline
    184847 & Henry VI, Part 3 \\ \hline
    10701462 & List of birds of Zambia \\ \hline
    10930255 & List of birds of Zimbabwe \\ \hline
    10930111 & List of birds of Mozambique \\ \hline
    48711 & Oregon Trail \\ \hline
    31518964 & History of the Oregon Trail \\
    \hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{Top 10 Article Pair Titles}
\begin{tabular}{| l | c |}
    \hline
    \textbf{Article ID} & \textbf{Title} \\ \hline
[Early life and career of Marcus Aurelius, Marcus Aurelius]
[Private equity in the 2000s, History of private equity and venture capital]
[List of ethnic cleansings, Ethnic cleansing]
[Route of the Oregon Trail, Oregon Trail]
[English literature, British literature]
[Culture of the United States, Society of the United States]
[18th-century history of Germany, History of Germany]
[Insect morphology, Insect wing]
[Nutritional neuroscience, Nutrition and cognition]
[Philippine general election, 2004, Philippine presidential election, 2004]
[History of the Dallas Mavericks, Dallas Mavericks]
[May Bukas Pa, List of May Bukas Pa episodes]
[Individualist anarchism in the United States, Anarchism in the United States]
[Native Americans in the United States, Native American cultures in the United States]
[Hockey stick controversy, Hockey stick graph]
[Filioque, History of the Filioque controversy]
[Vancouver Canucks, History of the Vancouver Canucks]
[Silvio Berlusconi, Controversies surrounding Silvio Berlusconi]
[2007 suicide bombings in Iraq, List of terrorist incidents in Iraq in 2007]
[List of Canadian tornadoes and tornado outbreaks, List of 21st-century Canadian tornadoes and tornado outbreaks]
[Scotland in the modern era, History of Scotland]
[Reliability of Wikipedia, Criticism of Wikipedia]
[Imperial Roman army, Auxiliaries (Roman military)]
[Libertarian socialism, Libertarian Marxism]
[Arts in Australia, Culture of Australia]
[Canti (Leopardi), Giacomo Leopardi]
[Culture of England, Religion in England]
[Government of Mahmoud Ahmadinejad (2005–present), Foreign policy of Mahmoud Ahmadinejad]
[Economy of England in the Middle Ages, Economics of English towns and trade in the Middle Ages]
[Go Nagai bibliography, Go Nagai]
[Galvatron, Megatron]
[Wakfu (TV series), Wakfu]
[Isabela, Basilan, History of Basilan]
[List of Prison Break recurring characters, List of Prison Break minor characters]
[Interracial marriage, Miscegenation]
[List of Shakespearean characters (L–Z), List of Shakespearean characters (A–K)]
[Fascism and ideology, Fascism]
[Anarchism, History of anarchism]
[Ethnic groups in Ecuador, Ecuadorian people]
[History of painting, Western painting, 20th-century Western painting]
[Precipitation, Rain]
[Megaupload legal case, Megaupload]
[Anti-spam techniques, Anti-spam techniques (users)]
[History of the Detroit Tigers, Detroit Tigers]
[Yuko Kavaguti, Alexander Smirnov (figure skater)]
[San Francisco Giants, History of the San Francisco Giants]
[List of Deadliest Warrior episodes, Deadliest Warrior (season 1), Deadliest Warrior (season 3), Deadliest Warrior (season 2)]
[List of Reaper characters, Reaper (TV series)]
[Port of Tianjin operations and logistics, Port of Tianjin]
[Management of androgenic alopecia, Management of baldness]
[Legion of Super-Heroes, Legion of Super-Heroes (1958 team)]
[American rock, Rock music]
[One-Day Internationals in England in 2005, Test matches in England in 2005, Australian cricket team in England in 2005]
[Swedes, Sweden]
[Controversies surrounding the European sovereign-debt crisis, Policy reactions to the European sovereign-debt crisis, European sovereign-debt crisis, Economic reforms and recovery proposals regarding the European sovereign-debt crisis]
[List of Irish Americans, List of Americans of Irish descent]
[CIA leak scandal criminal investigation, Plame affair grand jury investigation]
[Medway watermills (lower tributaries), River Len]
[2000 New Year Honours, 1999 New Year Honours]
[Kingdom of Greece, History of modern Greece]
[List of Russian people, List of Russian scientists]

    %% 21986867 & 2000 New Year Honours \\ \hline
    %% 21986897 & 1999 New Year Honours \\ \hline
    %% 3951586 & Instruments of the United Kingdom, 1994 \\ \hline
    %% 3951664 & Instruments of the United Kingdom, 1995 \\ \hline
    %% 1903966 & Management of baldness \\ \hline
    %% 38088660 & Management of androgenic alopecia \\ \hline
    %% 1503105 & Jayne Torvill \\ \hline
    %% 1503115 & Christopher Dean \\ \hline
    %% 184843 & Henry VI, Part 1 \\ \hline
    %% 184846 & Henry VI, Part 2 \\ \hline
    %% 184847 & Henry VI, Part 3 \\ \hline
    %% 10701462 & List of birds of Zambia \\ \hline
    %% 10930255 & List of birds of Zimbabwe \\ \hline
    %% 10930111 & List of birds of Mozambique \\ \hline
    %% 48711 & Oregon Trail \\ \hline
    %% 31518964 & History of the Oregon Trail \\
    \hline
\end{tabular}
\end{table}
